Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2018-12-18 vesicle_code/docs/adhesion/adhesion.tex
worked on shear example

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially place symmetrically on the $y$ axis so that the background
velocity drives the vesicles towards one another.  We vary the reduced
area and the two vdW parameters and characterize the possible steady
state configurations.  For all the simulations, the length of the
vesicles are fixed, while the area is changed to achieve the desired
reduced area.

@@

\todo[inline]{Phase diagram of different shapes that can be formed}
\todo[inline]{Vary the reduced area, adhesion strength, and adhesion
length scale?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Formation of doublets}
\label{sec:sflow_doublet_formation} 
The formation of the doublet depends on four main parameters: the
vesicles' reduced area, the adhesion length scale $\delta$, the adhesion
strength $\sigma$, and the shear rate $\chi$.
Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
have formed a doublet at several instances in time.  The double
structure affects the rheological properties of the flow; in particular,
it increases the effect viscosity as discussed in Section~\ref{}.  In
Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
distance between the two vesicles as a function of time for various
adhesion strengths.  The adhesion strength corresponding to the red
curves is less than a critical strength $\sigma_c$ for a doublet to
form.  In contrast, for larger adhesive strengths, doublets are formed
(blue curves).

@@

\begin{figure}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \caption{{\em Left}: Distance between a pair of vesicles in a planar
    shear flow with shear rate $\chi=1$ and adhesion length scale
    $\delta = 0.4$.   The different lines correspond to a linear spacing
    of adhesion strengths ranging from $\sigma=0.1$ and $\sigma=1.0$.
    {\em Right}: Phase diagram of vesicle hydrodynamics in a shear flow.
    At a fixed reduced area $\triangle A=0.90$ and $\delta =0.4$,  the
    critical vdW potential strength $\sigma$ for binding of two vesicles
    in a shear flow depends on the shear rate $\chi$.
  \label{fig:sflow_phase_diagram}}
\end{figure}

@@

\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame412.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame2565.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame3611.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame4075.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame6501.png}
%\includegraphics[keepaspectratio=true,scale=0.215]{figs/shear2Ves03na_frame6640.png}
\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.7$ and $\triangle A=0.95$.}
\label{fig:sflow_1frames}
\end{figure}

\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame12630.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame15128.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame18399.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame18801.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame19018.png}
%\includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03qa_frame21547.png}
\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 1.0$ and $\triangle A=0.95$.}
\label{fig:sflow_2frames}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of reduced area}
%\label{sec:sflow_reduced_area} 
%Figure~\ref{fig:sflow_ra_D12} and~\ref{fig:sflow_shearVes11frames}
%
%\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.405]{figs/shear2Ves10-11D12a.eps}
%\includegraphics[keepaspectratio=true,scale=0.405]{figs/shear2Ves10-11tau.png}
%\caption{Dynamics of two vesicles in a shear flow with the adhesion length $\delta = 0.4$ and several varying adhesion strength $\sigma$. Tolerance in length error is $10^{-3}$ and number of points is $256$ on each vesicle.}
%\label{fig:sflow_ra_D12}
%\end{figure}
%
% \begin{figure}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6026.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6144.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6704.png}\\
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame6945.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame7463.png}
% \includegraphics[keepaspectratio=true,scale=0.27]{figs/shear2Ves03etol1em3_frame7986.png}
% \caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.1$ and $\triangle A=0.95$.}
% \label{fig:sflow_shearVes03eframes}
% \end{figure}
%
%\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame2287.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame2927.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame3855.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4072.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4108.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4281.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame4676.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame5001.png}
%\includegraphics[keepaspectratio=true,scale=0.2]{figs/shear2Ves02qe_frame5070.png}
%\caption{Dynamics of a vesicle doublet in a shear flow with $\delta = 0.4$, $\sigma = 0.1$ and $\triangle A=0.5$.}
%\label{fig:sflow_shearVes11frames}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effective viscosity of a doublet}
\todo[inline]{Effect of effective viscosity with respect to the reduced
area and adhesion model}
\todo[inline]{Compare a single vesicle as per Misbah with doublets}
\todo[inline]{Bryan can start this section}

Here we investigate rheology of suspensions by computing the effective
viscosity. The effective viscosity is defined as the viscosity of a
homogeneous Newtonian fluid with the same energy dissipation per
macroscopic element of fluid.  In a simple shear flow, the ambient
velocity field is given by $\uu(\xx) = (\chi y,0)$, where $\chi$ is the
shear rate.  In dilute suspensions, the interaction between vesicles can
be ignored, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.  For dilute suspensions of rigid
bodies, the intrinsic viscosity was derived by Eienstein~\cite{}, and it
is given by
\begin{align*}
  something.
\end{align*}
For vesicles, the intrinsic viscosity was derived by Misbah~\cite{}, and
it is given by
\begin{align*}
  something.
\end{align*}
\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
\end{figure}

When adhesion is present, the formation of doublets has a significant
effect on the effective viscosity.

>>>>

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially place symmetrically on the $y$ axis so that the background
velocity drives the vesicles towards one another.  We vary the reduced
area and the two vdW parameters and characterize the possible steady
state configurations.  For all the simulations, the length of the
vesicles are fixed, while the area is changed to achieve the desired
reduced area.

@@

@@

The formation of the doublet depends on four main parameters: the
vesicles' reduced area, the adhesion length scale $\delta$, the adhesion
strength $\sigma$, and the shear rate $\chi$.
Figure~\ref{fig:doublet090} shows the configuration of two vesicles that
have formed a doublet at several instances in time.  In
Figure~\ref{fig:sflow_phase_diagram} (left), we show the minimum
distance between the two vesicles as a function of time for various
adhesion strengths.  The adhesion strength corresponding to the red
curves is less than a critical strength $\sigma_c$ for a doublet to
form.  In contrast, for larger adhesive strengths, doublets are formed
(blue curves).

@@

\begin{figure}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.4\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \caption{{\em Left}: Distance between a pair of vesicles in a planar
    shear flow with shear rate $\chi=0.5$ and adhesion length scale
    $\delta = 0.4$.   The different lines correspond to a linear spacing
    of adhesion strengths ranging from $\sigma=0.1$ and $\sigma=1.0$.
    {\em Right}: Phase diagram of vesicle hydrodynamics in a shear flow.
    At a fixed reduced area $\triangle A=0.90$ and $\delta =0.4$,  the
    critical vdW potential strength $\sigma$ for binding of two vesicles
  in a shear flow depends on the shear rate $\chi$.
\label{fig:sflow_phase_diagram}}
\end{figure}

@@

We investigate rheology of suspensions by computing the effective
viscosity of a doublet and compare it to the effective viscosity of a
single tank-treading vesicle. The effective viscosity is defined as the
viscosity of a homogeneous Newtonian fluid with the same energy
dissipation per macroscopic element of fluid.  In a simple shear flow,
the ambient velocity field is given by $\uu(\xx) = \chi(y,0)$, where
$\chi$ is the shear rate, and the intrinsic viscosity is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 T} \int_{T_i}^{T_e} 
  \langle \sigma_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \sigma \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds.
\end{align*}
Here, $[\mu]$ is the intrinsic viscosity, $|phi$ is the area fraction of
vesicles, $\sigma$ is the stress due to the vesicles, and $\langle \cdot
\rangle$ is the spatial average.

\begin{figure}[htp]
  \includegraphics[scale=1]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} The intrinsic viscosity
  of a tank treading vesicle (blue) and a doublet (red).  The shear rate
is $\chi = 0.5$, the Hamaker constant is $\sigma = 0.7$, and the
adhesion length scale is $\delta = 0.4$.  The length of the vesicles at
each of the reduced areas is fixed, while the area changes with
differing reduced areas.}
\end{figure}
